---
title: "Hands-on_Ex4-2 Visualising Uncertainty"
editor: visual
author: "Han Shumin"
date: "5 May 2023"
execute: 
  warning: false
---

## 10.1 Learning Outcome

## 10.2 Visualizing the uncertainty of point estimates

-   A point estimate is a single number, such as a mean.

-   Uncertainty is expressed as standard error, confidence interval, or credible interval

-   Important:

    -   Don't confuse the uncertainty of a point estimate with the variation in the sample

```{r}
pacman::p_load(tidyverse, plotly, crosstalk, DT, ggdist, gganimate, ggplot2, dplyr)
```

```{r}
exam <- read_csv("data/Exam_data.csv")
```

### 10.2.1 Visualizing the uncertainty of point estimates: ggplot2 methods

The code chunk below performs the followings:

-   group the observation by RACE,

-   computes the count of observations, mean, standard deviation and standard error of Maths by RACE, and

-   save the output as a tibble data table called `my_sum`.

```{r}
my_sum <- exam %>%
  group_by(RACE) %>%
  summarise(
    n=n(),
    mean=mean(MATHS),
    sd=sd(MATHS)
    ) %>%
  mutate(se=sd/sqrt(n-1))
```

Note: For the mathematical explanation, please refer to Slide 20 of Lesson 4.

```{r}
knitr::kable(head(my_sum), format = 'html')
```

### 10.2.2 Visualizing the uncertainty of point estimates: ggplot2 methods

The code chunk below is used to reveal the standard error of mean maths score by race.

```{r}
ggplot(my_sum) +
  geom_errorbar(
    aes(x=RACE, 
        ymin=mean-se, 
        ymax=mean+se), 
    width=0.2, 
    colour="black", 
    alpha=0.9, 
    size=0.5) +
  geom_point(aes
           (x=RACE, 
            y=mean), 
           stat="identity", 
           color="red",
           size = 1.5,
           alpha=1) +
  ggtitle("Standard error of mean maths score by race")
```

### 10.2.3 Visualizing the uncertainty of point estimates: **ggplot2** methods

```{r}
my_sum_sorted <- my_sum %>% 
  arrange(desc(mean)) %>%
  mutate(RACE = forcats::fct_reorder(RACE, -mean))


ggplot(my_sum_sorted) +
  geom_errorbar(
    aes(x=RACE, 
        ymin=mean-se, 
        ymax=mean+se), 
    width=0.2, 
    colour="black", 
    alpha=0.9, 
    size=0.5) +
  geom_point(aes
           (x=RACE, 
            y=mean), 
           stat="identity", 
           color="red",
           size = 1.5,
           alpha=1) +
  ggtitle("Standard error of mean maths score by race")

```
